NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PS lipids

### 2018-09-14 Manuscript/manuscriptPS.tex
Add CHARMM36 data with additional potassium

@@

>>>>

    POPC:POPS (5:1)/K$^+$  & CHARMM36 \cite{klauda10,venable13} &0.45 & 0 & 110:22 & 4926  & 40 & 298  & 200 & 150 & \cite{charmm36pops+83popcT298KwithK}  \\
    POPC:POPS (5:1)/K$^+$  & CHARMM36 \cite{klauda10,venable13} &0.89 & 0 & 110:22 & 4946  & 79 & 298  & 200 & 150 & \cite{charmm36pops+83popcT298KwithK}  \\

@@

    POPC:POPS (5:1)/K$^+$  & CHARMM36 \cite{klauda10,venable13} &0.44 & 0 & 110:22 & 4965  & 39 & 298  & 200 & 150 & \cite{charmm36pops+83popcT298KwithNa}  \\
    POPC:POPS (5:1)/K$^+$  & CHARMM36 \cite{klauda10,venable13} &0.89 & 0 & 110:22 & 4932  & 79 & 298  & 200 & 150 & \cite{charmm36pops+83popcT298KwithNa}  \\
